The expected shape of the Milky Way's Dark Matter halo

### 2019-02-05 Paper/paper.tex
compila

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{subfig}
\usepackage{array}

% Included by user
\usepackage{multirow}
\usepackage{multicol}
\usepackage{blindtext}
\newcolumntype{?}{!{\vrule width 1pt}}

\newenvironment{Table}
   {\par\bigskip\noindent\minipage{\columnwidth}\centering}
   {\endminipage\par\bigskip}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[MW DM halo shape in AURIGA]{The expected shape of the Milky Way's Dark Matter halo}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\', Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

@@

In this work we use the results of the state-of-the art Auriga
simulations \citep{auriga}. 
The objects in those simulations were selected from a set of 30 isolated halos in
the Evolution and Assembly of GaLaxies and their Environments (EAGLE)
project \citep{Eagle}. 
These halos were randomly selected from a sample of the most isolated
quartile of halos whose virial mass $M_{200}$ varied between
$10^{12}M_\odot$ and $2\times 10^{12}M_\odot$. 
These halos were re-simulated with higher resolution an varying
physical realism using the AREPO code \citep{arepo}.

@@

@@

\begin{figure*}
  \centering
  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
  \hfill
  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
  \hfill
  \caption{DM density for inner/outer (left/right panel) DM halo regions.}
  \label{fig:slices}
\end{figure*}

@@

\begin{figure}
\centering
{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.}
\label{fig:DM_MHD}
\end{figure}

\begin{figure}
  \centering
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}

  \hfill
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar shows median and errors for each sampled radii. }
  \label{fig:Triax_DM}
\end{figure}

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is
  not clear. Some studies claim that the DM halo must be oblate, at
  least in the vicinities of the disk, to ensure its stability
  \cite{disk stability}. However,)))} not much is said about its
dependence with radius as previous studies focus rather on the effects
of baryons on the dynamics of the halo at fixed radii. Examining the
representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
some things are noticeable: first, the DM halo is almost perfectly
oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

\begin{figure}
  \centering
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
  \hfill
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. Errorbar
    shows median and errors for each sampled radii. } 
  \label{fig:Triax_MHD}
\end{figure}

@@

As a check of consistency, we compare our new isopotential shape
results with the analytic expression of the
$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep[Binney and Tremaine
  year]{Binney and tremaine}, taking the volume-enclosed axial ratios
as an approximation for the isodensity contour ratios
$q_{\rho}$. Although this analytic expression if meant to be used for
logarithmic axisymmetric halos, it works well as a first approximation
for nearly axisymmetric halos as those produced by our disced
galaxies. We find that the difference between the real and the
analytic isopotential axial ratios is not bigger than $quantity
percent$. With this, we may now present on table
\ref{tabe:isopotential} our observationally-comparable results for MHD
halos at two important radii one corresponding to the approximate
regimes where the MW DM halo is usually constrained.

@@

\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
    \label{fig:Star_Density_effect}
\end{figure}

@@

\subsection{The historical shape}
One of the principal motivations to study the radial dependence of the
DM halo shape is that it may encode some clues about its formation
history. We have already shown that DM-only halos seem to exhibit a
steady and monotonous growth in its axial ratios when sampled at
bigger radii. One similar effect can be found if we sample the shape
at the virial radius, this time at varying redshift. It is easy to see
that the axial ratios increase with decreasing redshift, which is
expected by the continuous influence of the gravitational potential
\cite{VeraCiro}. In figure \ref{fig:RedshiftGood} we present a
representative example.

\begin{figure}
  \centering
  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \hfill
  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in terms of redshift (color). This halo maintains its shape until $z\approx 1$ obviating the systematic rounding effect in time from asymmetric potentials. }
  \label{fig:RedshiftGood}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs Star Density of the simulation.}
    \label{fig:DM Z Triax}

\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
    \caption{Difference in asphericities between MHD and DM shapes Vs
      Star Density of the simulation.} 
    \label{fig:MHD Z Triax} 
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[Perfectly aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
  \hfill
  \subfloat[Somewhat aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
  \hfill
  \subfloat[Chaotic Axes]{\includegraphics[width=1\columnwidth]{./pics/chaotic_axes.png}}
  \hfill
  \caption{Description of axes alignments }
  \label{fig:alignment}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}

\end{document}

% End of mnras_template.tex

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{subfig}
\usepackage{array}

\usepackage{multirow}
\usepackage{multicol}
\usepackage{blindtext}
\newcolumntype{?}{!{\vrule width 1pt}}

\newenvironment{Table}
   {\par\bigskip\noindent\minipage{\columnwidth}\centering}
   {\endminipage\par\bigskip}

\title[MW DM halo shape in AURIGA]{The expected shape of the Milky Way's Dark Matter halo}

\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\', Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

@@

In this work we use the results of the state-of-the art Auriga
simulations \citep{auriga}. 
The objects in those simulations were selected from a set of 30
isolated halos in the Evolution and Assembly of GaLaxies and their
Environments (EAGLE)  project \citep{Eagle}.   
These halos were randomly selected from a sample of the most isolated
halos whose virial mass $M_{200}$ varied between $10^{12}M_\odot$ and
$2\times 10^{12}M_\odot$. 
These halos were re-simulated with higher resolution an varying
physical realism using the AREPO code \citep{arepo}.

@@

\begin{table*}
\centering
\begin{tabular}{l|cc|cc|cc|cc}
\hline
\hline
Halo & \multicolumn{2}{c}{$N_P$/$10^6$} & \multicolumn{2}{c}{$M_P$/$10^5M_\odot$} & 
\multicolumn{2}{c}{$R_{vir}$/Kpc} & \multicolumn{2}{c}{$M_{vir}$/$10^{14} M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 1&4.068&2.447&2.397&2.022&196.927&187.674&9.062&7.844\\
halo 2&5.625&5.457&2.481&2.093&235.094&233.934&15.418&15.191\\
halo 3&3.826&3.852&2.645&2.231&210.693&210.955&11.099&11.141\\
halo 4&4.585&4.530&2.590&2.185&219.378&215.438&12.529&11.866\\
halo 5&3.262&3.290&2.533&2.137&196.984&197.246&9.071&9.106\\ \hline
halo 6&3.184&3.110&2.337&1.972&191.840&189.342&8.378&8.054\\ \hline
halo 7&3.878&3.729&2.296&1.937&197.864&196.509&9.193&9.005\\
halo 8&2.772&2.796&2.451&2.068&190.716&191.764&8.231&8.368\\
halo 9&3.038&3.010&2.738&2.310&195.826&190.640&8.911&8.222\\
halo 10&2.700&2.751&2.541&2.144&187.139&188.147&7.777&7.904\\
halo 11&4.146&4.116&2.541&2.144&221.821&219.568&12.952&12.560\\
halo 12&2.865&2.908&2.645&2.231&192.280&192.038&8.436&8.404\\
halo 13&3.520&3.600&2.393&2.019&202.139&203.815&9.801&10.048\\
halo 14&4.200&4.475&2.499&2.108&215.535&218.927&11.882&12.453\\
halo 15&2.888&2.845&2.541&2.144&199.848&200.658&9.471&9.588\\ \hline
halo 16&3.821&3.871&2.499&2.108&212.590&212.632&11.401&11.408\\ \hline
halo 17&2.752&2.781&2.552&2.153&188.067&187.404&7.893&7.811\\
halo 18&3.770&3.624&2.738&2.310&201.124&207.293&9.655&10.571\\
halo 19&2.989&3.086&2.645&2.231&200.244&200.325&9.527&9.540\\
halo 20&3.903&3.822&2.481&2.093&210.097&211.423&11.005&11.214\\ \hline
halo 21&4.105&4.075&2.640&2.227&219.527&219.823&12.555&12.604\\ \hline
halo 22&2.794&2.766&2.625&2.215&188.363&184.801&7.931&7.489\\ \hline
halo 23&3.977&4.073&2.795&2.358&217.768&215.959&12.254&11.952\\\hline
halo 24&4.466&4.426&2.522&2.127&217.440&215.147&12.199&11.817\\ \hline
halo 25&2.902&2.806&2.645&2.231&199.922&198.299&9.482&9.254\\
halo 26&4.610&4.716&2.506&2.115&219.984&218.939&12.633&12.454\\\hline
halo 27&5.060&5.018&2.590&2.185&228.036&226.225&14.071&13.740\\ \hline
halo 28&4.184&4.276&2.645&2.231&216.979&217.997&12.121&12.294\\
halo 29&4.827&4.613&2.499&2.108&225.791&219.935&13.660&12.625\\
halo 30&3.268&3.112&2.579&2.176&195.043&194.741&8.805&8.763\\
\hline
\hline
\end{tabular}
\caption{Specifications of each level 4 galaxy (halo). The DM and MHD versions of each parameters are presented together. The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
\label{tab:level4}
\end{table*}

\begin{table*}
\centering
\begin{tabular}{l?cc?cc?cc?cc}
\hline
\hline
Halo & \multicolumn{2}{c?}{$N_P$/$10^6$} & \multicolumn{2}{c?}{$M_P$/$10^5M_\odot$} & \multicolumn{2}{c?}{$R_{vir}$/Kpc}&\multicolumn{2}{c}{$M_{vir}$/$10^{14}M_\odot$}  \\ \hline
& DM & MHD& DM & MHD& DM & MHD& DM & MHD\\ \hline \hline
halo 6&24.902&24.185&0.292&0.246&191.741&188.367&8.365&7.932\\
halo 16&29.750&30.334&0.312&0.263&212.622&212.542&11.406&11.395\\
halo 21&31.993&31.503&0.330&0.278&219.731&220.250&12.588&12.679\\
halo 23&31.379&31.618&0.349&0.295&217.793&213.358&12.259&11.524\\
halo 24&34.987&35.153&0.315&0.266&217.313&213.963&12.179&11.624\\
halo 27&39.617&39.056&0.324&0.273&227.908&223.484&14.048&13.244\\
\hline
\hline
\end{tabular}
\caption{Specifications of each level 3 galaxy (halo). The DM and MHD versions of each parameters are presented together. The columns of this table indicate: (1) Halo name, (2,3) Number of (millions) of DM particles belonging to the halo, (4,5) Mass per particle in $10^5M_\odot$, (6,7) Virial radius (R TopHat 200) of the halo in Kpc, (8,9) Virial mass of the halo in $10^{14}M_\odot$.}
\label{tab:level3}
\end{table*}

@@

\begin{figure*}
  \centering
  \subfloat[halo 27 DM shape at small radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_inner.png}}
  \hfill
  \subfloat[halo 27 DM shape at big radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_27_outter.png}}
  \hfill
  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
  Slice 20 percent of the max-min range in the "z" position of
  particles belonging to the main structure, centered at halo defined
  position (calculated with most bounded particle) }  
  \label{fig:slices}
\end{figure*}

@@

\begin{figure}
\centering
{\includegraphics[width=0.8\columnwidth]{./pics/halo16.png}}
\caption{Radial profile for axial ratios and the triaxiality parameter $T=\frac{1-b/a}{1-c/a}$ for halo 16.
Radial profile was sampled at redshift 0 and there are two sets of
lines showing MHD and DM-only versions of the axial ratios profile}
\label{fig:DM_MHD}
\end{figure}

\begin{figure}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (DM only)
   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.
  Errorbar shows median and errors for each sampled radii.
  Conclusion: DM halos are rounder on the outskirts}
  \label{fig:Triax_DM}
\end{figure}

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is
  not clear. Some studies claim that the DM halo must be oblate, at
  least in the vicinities of the disk, to ensure its stability
  . However,)))} not much is said about its
dependence with radius as previous studies focus rather on the effects
of baryons on the dynamics of the halo at fixed radii. Examining the
representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
some things are noticeable: first, the DM halo is almost perfectly
oblate around $\approx 10-30$Kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50Kpc$ and below $10Kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

\begin{figure}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (MHD only)
   Each dot represents the shape characterization of each halo at the
   2 times the virial radius and a  1/16 fraction of the virial radius
   differentiated by color. 
  Errorbar shows median and errors for each sampled radii.
  Conclusion: MHD halos are more oblate on the outer skirts: b/a
  changes while c/a remains practically constant (on average)}
  \label{fig:Triax_MHD}
\end{figure}

@@

As a check of consistency, we compare our new isopotential shape
results with the analytic expression of the
$(1-q_{\phi})\frac{1}{3}(1-q_{\rho})$ \citep{Binney_and_Tremaine_2008}, taking the volume-enclosed axial ratios
as an approximation for the isodensity contour ratios
$q_{\rho}$. Although this analytic expression if meant to be used for
logarithmic axisymmetric halos, it works well as a first approximation
for nearly axisymmetric halos as those produced by our disced
galaxies. We find that the difference between the real and the
analytic isopotential axial ratios is not bigger than $quantity
percent$. With this, we may now present on table
\ref{tabe:isopotential} our observationally-comparable results for MHD
halos at two important radii one corresponding to the approximate
regimes where the MW DM halo is usually constrained.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
  \caption{Difference in asphericities between MHD and DM shapes Vs
    Star Density of the simulation. Unsure about this graphic. Take
    delta asphericity as the strength of the rounding effect of
    baryons.}  
  \label{fig:Star_Density_effect}
\end{figure}

@@

\subsection{The historical shape}
One of the principal motivations to study the radial dependence of the
DM halo shape is that it may encode some clues about its formation
history. We have already shown that DM-only halos seem to exhibit a
steady and monotonous growth in its axial ratios when sampled at
bigger radii. One similar effect can be found if we sample the shape
at the virial radius, this time at varying redshift. It is easy to see
that the axial ratios increase with decreasing redshift, which is
expected by the continuous influence of the gravitational potential
\cite{Vera-Ciro_et_al._2011}. In figure \ref{fig:RedshiftGood} we
present a representative example.

\begin{figure}
  \subfloat[halo 16 DM]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_DM_Z.png}}
  \subfloat[halo 16 MHD]{\includegraphics[width=0.5\columnwidth]{./pics/Redshift/halo_16_level3_MHD_Z.png}}
  \caption{Radial profile (comoving) of axial ratios for halo 16 in
    terms of redshift (color). This halo maintains its shape until
    $z\approx 1$ obviating the systematic rounding effect in time from
    asymmetric potentials. Each plot-line represents the radial
    profile at a determined redshift. Conclussion: Mainly for b/a, it increases for:
    (1) for bigger radii (fixed redshift)(2) for lower redshift (fixed
    radius) It explains the correlation between radial profile and
    history, but does not require that curves match in the triaxial
    plane.}
  \label{fig:RedshiftGood}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
  \caption{DM only Radial profile at redshift 0 (dashed line)
    Historical profile at virial radius R500 (colour line). Example
    of a halo where there is some correlation between these two
    profiles, as usually happens for DM only
    simulations. Conclusion: DM only halos usually (fraction?) have
    correlated shape profiles.} 
  \label{fig:DM Z Triax}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
  \caption{MHD. Radial profile at redshift 0 (dashed line)
    Historical profile at virial radius R500 (colour line)
    Example of a halo where there is no correlation
    between these two profiles, as usually happens in
    MHD. Conclusion: MHD halos usually (fraction?) have uncorrelated shape profiles.}
    \label{fig:MHD Z Triax} 
\end{figure}

@@

\begin{figure}
  \centering
  \subfloat[Perfectly aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/well_axes.png}}
  \hfill
  \subfloat[Somewhat aligned Axes]{\includegraphics[width=1\columnwidth]{./pics/rotating_axes.png}}
  \hfill
  \subfloat[Chaotic Axes]{\includegraphics[width=1\columnwidth]{./pics/chaotic_axes.png}}
  \hfill
  \caption{Star: Minor Axis
    Triangle: Medium Axis
    Square: Major Axis
    Color: Radii at which shape was sampled (show radii sampled)
    Contour color: If orientation is above or below in this projection
    Cross (black): Orientation of the stellar disk
    Conclusion: Axes (minor) are not (generally) aligned with the
    stellar disk nor are they usually aligned with each other from
    different radii. We show some cases that may happen.} 
  \label{fig:alignment}
\end{figure}

@@
